Output Summary

### 2021-09-21 03-post-process/output-plots.Rmd
add decomposition of vcov to output plots

---
title: "Output Summary"
subtitle: "Multi-Population Model"
output: 
  html_document:
    toc: true
    toc_float: true
params:
  scenario:
    label: "Scenario"
    value: "base"
    input: text
editor_options: 
  chunk_output_type: console
---

@@

# extract the two key structures from this object
post = model_info$post
# post = post_thin(model_info$post, keep_percent = 0.1)  # uncomment this to run document with 10% of the retained MCMC samples
jags_data = model_info$jags_data

# the years included by the model
all_yrs = as.numeric(dimnames(jags_data$Pa_obs)[[1]])

# which years are "observable" for at least some quantities?
observable = (jags_data$kmax+1):jags_data$ny
```

```{r dimension-ids}
# population names
pops = colnames(jags_data$Ra_obs)

@@

>>>>

---
title: "Output Summary"
subtitle: "Multi-Population Model"
output: 
  html_document:
    toc: true
    toc_float: true
params:
  scenario:
    label: "Scenario"
    value: "complex-ocean-survival-with-prior"
    input: text
editor_options: 
  chunk_output_type: console
---

@@

# extract the two key structures from this object
post = model_info$post
# post = post_thin(model_info$post, keep_percent = 0.1)  # uncomment this to run document with 10% of the retained MCMC samples
jags_data = model_info$jags_data
```

```{r dimension-ids}
# the years included by the model
all_yrs = as.numeric(dimnames(jags_data$Pa_obs)[[1]])

# which years are "observable" for at least some quantities?
observable = (jags_data$kmax+1):jags_data$ny

# population names
pops = colnames(jags_data$Ra_obs)

@@

```{r vcov-decomp, message = FALSE}
# Convert the precision matrices monitored by JAGS into the marginal SD and correlation matrix terms
# postpack::vcov_decomp() does this for all posterior samples

Sig_Lphi_O0_O1_post = suppressMessages(vcov_decomp(post, "Sig_Lphi_O0_O1", invert = FALSE, sigma_base_name = "sig_Lphi_O0_O1", rho_base_name = "rho_Lphi_O0_O1"))

# make the labels/indices for which elements of the vcov matrices contain unique covariances
# no point in summarizing/displaying both off-diagonal triangles
dummy_cols = matrix(rep(1:jags_data$nj, each = jags_data$nj), jags_data$nj, jags_data$nj)
dummy_rows = matrix(rep(1:jags_data$nj, jags_data$nj), jags_data$nj, jags_data$nj)
vcov_cols = dummy_cols[lower.tri(dummy_cols)]
vcov_rows = dummy_rows[lower.tri(dummy_rows)]
vcov_labels = paste0(pops[vcov_rows], "-", pops[vcov_cols])
vcov_indices = paste0("[", vcov_rows, ",", vcov_cols, "]")

# subset out only the unique elements
Sig_Lphi_O0_O1_post = post_subset(Sig_Lphi_O0_O1_post, c("sig", paste0("rho.+", vcov_indices)))

# combine these derived posterior samples with the main object
post = post_bind(post, Sig_Lphi_O0_O1_post)
```
